---
name: Cristina
surname: Marchant
position: "Sociologist, MA in Design and Analysis of Social Surveys"
address: "Santiago, Chile"
email: "cemarcha@uc.cl"
github: cristinamarchant
linkedin: cristinamarchant
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Education

```{r}
library(tibble)
tribble(
  ~ Grado, ~ Ano, ~ Institucion, ~ donde,
  "Sociologist", "2014", "Pontifical Catholic University of Chile", "Santiago, Chile",
  "Master's Degree in Design and Analysis of Social Surveys", "2018", "Pontifical Catholic University of Chile", "Santiago, Chile") %>% 
  detailed_entries(Grado, Ano, Institucion, donde)
```

## Student Exchange

```{r}
tribble(
  ~ Grado, ~ Ano, ~ Institucion, ~ donde,
  "Sociology", "2013-2014", "Università degli Studi di Bologna", "Bologna, Italia") %>% 
  detailed_entries(Grado, Ano, Institucion, donde)
```

# Work Experience

&nbsp;

## October 2018 - To date

**Project Manager at the Social Studies Directorate**, Institute of Sociology of  Pontifical Catholic University of Chile (DESUC).

Project coordination, quantitative and qualitative data analysis, sample designs, weights design, quality control and questionnaire design.

```{r}
tribble(
  ~Ano, ~Estudio, ~Mandante,
  2021, "National Bicentennial Survey 2021", "CPP UC",
  2021, "Quality of Life and Health Measurement Survey", "ACHS Chile",
  2021, "Conecta Mayor Program Impact Evaluation Fieldwork", "Conecta Mayor Foundation",
  2021, "National Television Survey 2021", "National Television Council",
  2020, "Pride of Chile Study, second version", "Imagen de Chile Foundation",
  2020, "Diversity and Discrimination Survey of LGBTIQ+ People", "Undersecretariat for Crime Prevention",
  2020, "Sample design of the Chile a Escala Project: We have to talk about Chile", "CPP UC",
  2020, "National Human Rights Survey 2020", "INDH",
  2019, "Survey on Forms of Violence and Exercise of Human Rights in Prioritized Neighborhoods", "INDH",
  2019, "National Survey on Quality of Life in the Elderly in Chile", "CEVE UC",
  2019, "National Survey on Access to Justice", "Judicial Power",
  2019, "Study Characterization of the MR (Metropolitan Region) Urban Park Network Users", "MINVU",
  2019, "Study of Tobacco Consumption in Chile", "MIDE UC",
  2019, "MR Business and Human Capital Study", "CPP UC and SENCE",
  2019, "National Survey of Digital School Development 2019", "MINEDUC",
  2019, "Vulnerability in the Chilean Elderly:  A Life Course Study of Accumulated Advantages and Disadvantages - Fondecyt", "Ignacio Madero",
  2018, "V National Survey on Democracy Auditing", "UNDP",
  2018, "Neighborhood Coexistence and Interculturality Survey", "Undersecretariat for Crime Prevention",
  2018, "Public Prosecutor's Office Institutional Perception and Positioning Study", "Public Prosecutor's Office",
) %>% 
  brief_entries(
    glue::glue("Coordination: {Estudio}"),
    Ano, 
    Mandante
  )
```

&nbsp;
&nbsp;

\newpage

## April - September 2018

**Consultant at Cliodinámica Ltda.**, a consulting firm dedicated to social studies and impact assessments in the public and private sectors.

Participation in projects, quantitative and qualitative data analysis, and participation in questionnaire design such as:

```{r}
tribble(
  ~Ano, ~Estudio, ~Mandante,
  2018, "National Human Rights Survey 2018", "INDH",
  2018, "Impact Evaluation of the Renueva tu Micro (Renew your Bus) Program", "Ministry of Transportation and Telecommunications",
  2018, "Evaluation of the Mejores Ferias para Santiago (Better Market Fairs for Santiago) Program", "FOSIS",
  2018, "Systematization and Analysis of FOSIS I.D.E.A. Programs", "FOSIS") %>% 
  brief_entries(
    glue::glue("Participation: {Estudio}"),
    Ano, 
    Mandante
  )
```

&nbsp;
&nbsp;


## March 2015 - March 2018

**Data analyst at the Social Studies Directorate**, Institute of Sociology of la Pontifical Catholic University of Chile (DESUC).

Project coordination, quantitative and qualitative data analysis, and participation in questionnaire design. 

```{r}
tribble(
  ~Ano, ~Estudio, ~Mandante,
  2018, "Public Defender's Office Service Perception Opinion Survey", "Public Defender's Office",
  2017, "First National Survey on Polyvictimization in Children and Adolescents", "Undersecretariat for Crime Prevention",
  2017, "Study on Reasons for Use of Presential Procedures", "SegPres",
  2016, "National Survey on Quality of Life and Health ENCAVI 2016", "Ministry of Health",
  2016, "National Survey on Environment and Climate Change 2016", "Ministry of the Environment",
  2016, "National Survey of Citizen Rights 2016", "SegPres",
  2016, "First National Survey of Scientific Culture: Social Perception of Science and Technology in Chile", "Conicyt",
  2016, "Study on Educational Quality from the Perception of Key System Stakeholders", "Agency for Quality Education",
  2016, "Survey on Perception of Security for Lo Barnechea Commune", "Lo Barnechea Security",
  2016, "Work Climate Measurement for Codelco in its ten divisions and work centers", "Codelco",
  2016, "First Index Study of Women in Senior Management", "Businesswomen",
  2015, "Third National Survey on Violence in the School Environment", "Undersecretariat for Crime Prevention",
  2015, "Stadium Safety Study Baseline", "Undersecretariat for Crime Prevention",
  2015, "National Survey on the trial phase of the National System of Quality Assurance in Key System Stakeholders", "Education Quality Agency") %>% 
  brief_entries(
    glue::glue("Participation: {Estudio}"),
    Ano, 
    Mandante
  )
```

\newpage

# Academic Experience

```{r}
tribble(
  ~ Institucion, ~ Ano, ~ Cargo,
  "Pontifical Catholic University of Chile", "2021", "Field Test Design and Analysis Professor",
  "Pontifical Catholic University of Chile", "2019", "Social Research Methodology Professor",
  "Master in Design and Analysis of Social Surveys, Pontifical Catholic University of Chile", "2019", "Teaching Assistant to Survey Sampling",
  "Pontifical Catholic University of Chile", "2016", "Teaching Assistant to the course Food and Society",
  "Pontifical Catholic University of Chile", "2014", "Teaching Assistant to the course Political Sociology",
  "Pontifical Catholic University of Chile", "2014", "Teaching Assistant to the course of Logic") %>% 
  detailed_entries(Institucion, Ano, Cargo)
```

# Work skills

## Software

* **R** for statistical analysis, database processing and data visualization: Advanced Level.
* **SPSS** for statistical analysis: Advanced level. 
* **Stata** for statistical analysis: Intermediate level.
* **DeDoose** for qualitative analysis: Intermediate level.
* **Microsoft Word, Excel and Power Point**: Advanced level.

## Languages

* Spanish: Native
* English: Advanced
* Italian: Advanced
